Title

### 2013-03-12 inc/model_results/shapes/shapes.tex
minor changes to shapes section

For an electron pulse with a higher initial space-charge density, intra-pulse Coulomb effects can dominate the propagation dynamics.
\ref{fig:compare_shape}\subref{fig:compare_shape_N1e6}, shows the predicted temporal dynamics of electron pulses with the same initial size and photoemission conditions as \ref{fig:compare_shape}\subref{fig:compare_shape_N1}, but with $ N = 10^{6} $ electrons --- the number required for single-shot diffraction pattern measurements in a DTEM.\cite{berger_dc_2009,armstrong_practical_2007}
The significant influence of space-charge effects for the higher initial peak pulse charge density is clearly evident.
%TODO revisit this next sentance, the data doesn't seem to bear it out
In the spherical case, space-charge induced bunch broadening overwhelms the initial difference between $\eta_{\smallT}$ and $\eta_{z}$, producing an almost uniform three-dimensional `Coulomb explosion' of the electron pulse with a one-dimensional bunch broadening rate roughly one order of magnitude greater than that for $ N = 10^{0} $ (\ref{fig:compare_shape}\subref{fig:compare_shape_N1}).
For $ \xi (0) > 1 $ (or $ \xi (0) < 1 $), the smaller initial transverse (longitudinal) bunch dimension experiences the greatest relative expansion in free-space propagation. This is to be expected, because the initial $\eta_{\alpha}$ are non-zero (but comparable in magnitude) while Coulomb effects will produce differential pulse broadening in the dimension with the largest internal space-charge field (i.e., the dimension with the largest electrostatic potential gradient).
In fact, both the $ N = 10^{6} $ disk- and cigar-like pulse examples shown in \ref{fig:compare_shape}\subref{fig:compare_shape_N1e6} transition through a spherical bunch shape ($ \xi \approx 1 $) after a time of flight of $\sim$0.5ns, at which point the peak pulse charge density has already been reduced by a factor of $\sim$100.
The initial impulse induced by the strong space-charge field then provides for continued linear expansion (in time), resulting in a linear pulse chirp in the dimension associated with the smallest initial HW1/eM bunch width\cite{michalik_analytic_2006,berger_dc_2009} $ \sqrt{ 2 \sigma_{\alpha} (0) } $.

>>>>

For an electron pulse with a higher initial space-charge density, intra-pulse Coulomb effects can dominate the propagation dynamics.
\ref{fig:compare_shape}\subref{fig:compare_shape_N1e6}, shows the predicted temporal dynamics of electron pulses with the same initial size and photoemission conditions as \ref{fig:compare_shape}\subref{fig:compare_shape_N1}, but with $ N = 10^{6} $ electrons --- the number required for single-shot diffraction pattern measurements in a DTEM.\cite{berger_dc_2009,armstrong_practical_2007}
The significant influence of space-charge effects for the higher initial peak pulse charge density is clearly evident.
%TODO revisit this next sentance, the data doesn't seem to bear it out
In the spherical case, space-charge induced bunch broadening overwhelms the initial difference between $\eta_{\smallT}$ and $\eta_{z}$, producing an almost uniform three-dimensional `Coulomb explosion' of the electron pulse with a one-dimensional bunch broadening rate roughly one order of magnitude greater than that for $ N = 10^{0} $ (\ref{fig:compare_shape}\subref{fig:compare_shape_N1}).
For $ \xi (0) > 1 $ (or $ \xi (0) < 1 $), the smaller initial transverse (longitudinal) bunch dimension experiences the greatest relative expansion in free-space propagation. This is to be expected, because the initial $\eta_{\alpha}$ are non-zero (but comparable in magnitude) while Coulomb effects will produce differential pulse broadening in the dimension with the largest internal space-charge field (i.e., the dimension with the largest electrostatic potential gradient).
%TODO the following sentance appears not to be true, still perhaps should include something like it
%In fact, both the $ N = 10^{6} $ disk- and cigar-like pulse examples shown in \ref{fig:compare_shape}\subref{fig:compare_shape_N1e6} transition through a spherical bunch shape ($ \xi \approx 1 $) after a time of flight of $\sim$0.5ns, at which point the peak pulse charge density has already been reduced by a factor of $\sim$100.
The initial impulse induced by the strong space-charge field then provides for continued linear expansion (in time), resulting in a linear pulse chirp in the dimension associated with the smallest initial HW1/eM bunch width\cite{michalik_analytic_2006,berger_dc_2009} $ \sqrt{ 2 \sigma_{\alpha} (0) } $.
